### 2015-01-03 prelim/oral_prelim.tex
prelim files

\usepackage{cmbright}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

@@

\title[Spatiotemporal Modeling of Extreme Events] % (optional, use only with long paper titles)
{
  Spatiotemporal Modeling of Extreme Events
}
\author[S. Morris, B. Reich, and D. Cooley]{Samuel Morris (NC State), Brian Reich (NC State), and Dan Cooley (Colorado State)}
\institute[NCSU, CSU]{}
\date{JSM 2014, Boston}

@@

% \begin{frame}{Introduction to extremes}
%   \begin{itemize} \setlength{\itemsep}{0.5em}
%     \item Max-stable processes (Cooley et al., 2012):
%     \begin{itemize}
%       \item Consider a spatial process $x_t(\bs)$, $t = 1, \ldots, T$.
%       \item Let $M_T(\bs) = \left\{ \bigvee_{t=1}^T x_t(\bs_1), \ldots, \bigvee_{t=1}^T x_t(\bs_n) \right\}$
%       \item If there exists normalizing sequences $a_T(\bs)$ and $b_T(\bs)$ such
%       that for all sites, $\bs_i, i = 1, \ldots, d$,
%       \begin{align*}
%         a_T^{-1}(\bs) \left\{ M_T(\bs) - b_T(\bs) \right\} \converged Y(\bs)
%       \end{align*}
%       which has a non-degenerate distribution, then $Y(\bs)$ is a max-stable process.
%     \end{itemize}
%   \end{itemize}
% \end{frame}

@@

% \begin{frame}{Multivariate representations}
%   \begin{itemize}
%     \item Multivariate distributions:
%     \begin{itemize}
%       \item Assume common standardized max-stable marginal, like unit-Fr\'{e}chet
%       \begin{align*}
%         \Pr(Z < z) = exp(-z^{-1})
%       \end{align*}
%       \item The multivariate representation for the GEV is
%       \begin{align*}
%         \Pr(\bZ \le \bz)  &= G^*(\bz) = \exp(-V(\bz))\\
%                 V(\bs)    &= d \int_{\Delta_d} \bigvee_{i = 1}^d \frac{w_i}{z_i} H(\ddd w)
%       \end{align*}
%       where
%       \begin{itemize}
%         \item $\Delta_d = \{ \bw \in \calR^d_+ \mid w_1 + \cdots + w_d = 1\}$
%         \item $H$ is a probability measure on $\Delta_d$
%         \item $\int_{\Delta_d}w_i H(\ddd w) = 1 / d$ for $i = 1, \ldots, d$.
%       \end{itemize}
%     \end{itemize}
%   \end{itemize}
% \end{frame}

\begin{frame}{Multivariate analysis}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item Multivariate max-stable and GPD models have nice features, but they are
    \begin{itemize}
      \item computationally challenging to work with
      \item joint distribution only available in low dimension
    \end{itemize}
    \item Pairwise likelihood approach (Huser and Davison, 2014)
  \end{itemize}
\end{frame}

>>>>

% \usepackage{cmbright}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

@@

\title[Spatial methods for extreme value analysis] % (optional, use only with long paper titles)
{
  Spatial methods for extreme value analysis
}
\author[Samuel A. Morris]{Samuel A. Morris}
\institute[NCSU]{}
\date{January 9, 2015}

@@

\begin{frame}{Introduction to extremes}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item Max-stable processes (Cooley et al., 2012):
    \begin{itemize}
      \item Consider a spatial process $x_t(\bs)$, $t = 1, \ldots, T$.
      \item Let $M_T(\bs) = \left\{ \bigvee_{t=1}^T x_t(\bs_1), \ldots, \bigvee_{t=1}^T x_t(\bs_n) \right\}$
      \item If there exists normalizing sequences $a_T(\bs)$ and $b_T(\bs)$ such
      that for all sites, $\bs_i, i = 1, \ldots, d$,
      \begin{align*}
        a_T^{-1}(\bs) \left\{ M_T(\bs) - b_T(\bs) \right\} \converged Y(\bs)
      \end{align*}
      which has a non-degenerate distribution, then $Y(\bs)$ is a max-stable process.
    \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Multivariate representations}
  \begin{itemize}
    \item Multivariate distributions:
    \begin{itemize}
      \item Assume common standardized max-stable marginal, like unit-Fr\'{e}chet
      \begin{align*}
        \Pr(Z < z) = exp(-z^{-1})
      \end{align*}
      \item The multivariate representation for the GEV is
      \begin{align*}
        \Pr(\bZ \le \bz)  &= G^*(\bz) = \exp(-V(\bz))\\
                V(\bs)    &= d \int_{\Delta_d} \bigvee_{i = 1}^d \frac{w_i}{z_i} H(\ddd w)
      \end{align*}
      where
      \begin{itemize}
        \item $\Delta_d = \{ \bw \in \calR^d_+ \mid w_1 + \cdots + w_d = 1\}$
        \item $H$ is a probability measure on $\Delta_d$
        \item $\int_{\Delta_d}w_i H(\ddd w) = 1 / d$ for $i = 1, \ldots, d$.
      \end{itemize}
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Multivariate analysis}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item Multivariate max-stable and GPD models have nice features, but they are
    \begin{itemize}
      \item computationally challenging to work with
      \item joint distribution only available in low dimension
    \end{itemize}
    \item Bayesian hierarchical model
    \item Pairwise likelihood approach (Huser and Davison, 2014)
  \end{itemize}
\end{frame}
